

\begin{thebibliography}{99}

\bibitem{winters1960forecasting} Winters PR. Forecasting sales by exponentially weighted moving averages. Management Science, 1960, 6(3): 324-342.

\bibitem{hyndman2018forecasting} Hyndman RJ, Athanasopoulos G. Forecasting: principles and practice, 2nd edition. OTexts, 2018.

\bibitem{box2015time} Box GEP, Jenkins GM, Reinsel GC, Ljung GM. Time series analysis: forecasting and control, 5th edition. John Wiley \& Sons, 2015.

\bibitem{breiman2001random} Breiman L. Random forests. Machine Learning, 2001, 45(1): 5-32.

\bibitem{chen2016xgboost} Chen TQ, Guestrin C. XGBoost: a scalable tree boosting system. Proceedings of the 22nd ACM SIGKDD, 2016: 785-794.

\bibitem{cohen1988statistical} Cohen J. Statistical power analysis for the behavioral sciences, 2nd edition. Lawrence Erlbaum Associates, 1988.

\bibitem{fisher1925statistical} Fisher RA. Statistical methods for research workers. Oliver and Boyd, 1925.

\bibitem{kruskal1952use} Kruskal WH, Wallis WA. Use of ranks in one-criterion variance analysis. Journal of the American Statistical Association, 1952, 47(260): 583-621.

\bibitem{pedregosa2011scikit} Pedregosa F, Varoquaux G, Gramfort A, et al. Scikit-learn: machine learning in Python. Journal of Machine Learning Research, 2011, 12: 2825-2830.

\bibitem{seabold2010statsmodels} Seabold S, Perktold J. Statsmodels: econometric and statistical modeling with Python. Proceedings of the 9th Python in Science Conference, 2010.

\bibitem{mckinney2010data} McKinney W. Data structures for statistical computing in Python. Proceedings of the 9th Python in Science Conference, 2010: 51-56.

\bibitem{hunter2007matplotlib} Hunter JD. Matplotlib: a 2D graphics environment. Computing in Science \& Engineering, 2007, 9(3): 90-95.

\end{thebibliography}
